---
title: "OTPRL reward, model2, results, OT vs. PL"
output: html_notebook
# xinyuanyan
# April, 2021
---

### nb is created by xinyuan
### xinyuanyan2016@gmail.com

**April, 2021**

**Main reference** 

1. Fontanesi, L., Gluth, S., Spektor, M. S., & Rieskamp, J. (2019). A reinforcement learning diffusion decision model for value-based decisions. Psychonomic bulletin & review, 26(4), 1099-1121.
2. Wiehler, A., & Peters, J. (2020). Diffusion modeling reveals reinforcement learning impairments in gambling disorder that are linked to attenuated ventromedial prefrontal cortex value representations. bioRxiv.



Code is created and adapted by Xinyuan Yan, will be shared at her github website:
https://github.com/psywalkeryanxy

If you have any further questions, please email to me(xinyuanyan2016@gmail.com), I will provide help as much as I can ^_^





## Xinyuan, please first load the data from rstan you've saved
```{r}
rm(list = ls())
setwd("/Users/xinyuanyan/Documents/6_DATA_ANALYSIS_2021/")
fitmdd<- readRDS(file = "RL_PL_model_02.rds")
fithea<- readRDS(file = "RL_OT_model_02.rds")
```
transform to matrix format
```{r}
mat_fitmdd = as.matrix(fitmdd)
mat_fithea = as.matrix(fithea)
```
extract the parameters you will estimate
```{r}
learning_rate_pos0 = mat_fitmdd[grep("^alpha_pos_sb",colnames(mat_fitmdd))]
learning_rate_neg0 = mat_fitmdd[grep("^alpha_neg_sb",colnames(mat_fitmdd))]

drift_scaling0 = mat_fitmdd[grep("^drift_scaling_sbj",colnames(mat_fitmdd))]###

threshold0 = mat_fitmdd[grep("^threshold_sbj",colnames(mat_fitmdd))]###

ndt0 = mat_fitmdd[grep("^ndt_sbj",colnames(mat_fitmdd))]###
```
collect them and then write into excel
```{r}
model2_MDD = cbind(learning_rate_pos0,learning_rate_neg0, drift_scaling0, threshold0, ndt0)
View(model2_MDD)

#write.csv(model2_MDD,"model2_MDD.csv")
```


```{r}
learning_rate_pos1 = mat_fithea[grep("^alpha_pos_sb",colnames(mat_fithea))]
learning_rate_neg1 = mat_fithea[grep("^alpha_neg_sb",colnames(mat_fithea))]

drift_scaling1 = mat_fithea[grep("^drift_scaling_sbj",colnames(mat_fithea))]###

threshold1 = mat_fithea[grep("^threshold_sbj",colnames(mat_fithea))]###

ndt1 = mat_fithea[grep("^ndt_sbj",colnames(mat_fithea))]###

model2_HEA = cbind(learning_rate_pos1,learning_rate_neg1, drift_scaling1, threshold1, ndt1)
View(model2_HEA)
```
stats
```{r}
t.test(model2_HEA[,4],model2_MDD[,4],var.equal = FALSE)
```


